### 2018-02-01 includes/appendix.tex
Typos

\subsection{Translate}
We now prove that \textit{Translate} transforms constraints into
equisatisfiable constraints. From above, we only need to show that for
every expression $e$, the following is true: $\textit{Translate}(\eval
(e))$ = $\eval (\textit{Translate}(e))$. For now, we assume that
\textit{Translate} fixes the digits pointwise and we prove the
stronger fact that $\textit{Translate}$ also fixes characters
pointwise in any string expression. (I.e., $\textit{Translate}$ are
bijections and further that digits are not mapped to any other
character.)

@@

For \texttt{str.in.re} we had to show that a string literals $s$, is a
member of a regular expression $r$ if and only if
$\textit{Translate}(s)$ is a member of $\textit{Translate}{r}$ by
induction on regular expressions. For the inductive cases of
\texttt{str.to.int}, and \texttt{str.from.int} we needed to use the
fact that the digits were fixed pointwise.

>>>>

\subsection{Translate}
We now prove that \textit{Translate} transforms constraints into
equisatisfiable constraints. From above, we only need to show that for
every expression $e$, the following is true: $\textit{Translate}(\eval
(e))$ = $\eval (\textit{Translate}(e))$. For now, we assume that
\textit{Translate} fixes the digits pointwise and we prove the
stronger fact that $\textit{Translate}$ also fixes characters
pointwise in any string expression. (i.e., in bijections of character
sets used by $\textit{Translate}$ the digits are not mapped to any
other character.)

@@

For \texttt{str.in.re} we had to show that a string literals $s$, is a
member of a regular expression $r$ if and only if
$\textit{Translate}(s)$ is a member of $\textit{Translate}(r)$ by
induction on regular expressions. For the inductive cases of
\texttt{str.to.int}, and \texttt{str.from.int} we needed to use the
fact that the digits were fixed pointwise.
